Learning causal features with double regression

### 2019-05-16 paper/paper.tex
odds and ends in paper

\section{Experiments - simulated data}
Experiments on simulated data serve three goals: compare double regression with other known techniques (CCA, OLS, PLS...) both as regression and feature extraction methods, provide evidence for our claims on stability, invariance to environment, and behavior as a causal detector, and understand the strengths and limitations of double regression, and directions for future improvement.

@@

FC: insert comment about scaling sigmoids, and maybe something about uniform coeffs

>>>>

\section{Experiments - simulated data}
Experiments on simulated data serve three purposes: compare double regression with other known techniques (CCA, OLS, PLS...) both as a regression and a feature extraction method, measure its performance for various values of its parameters and provide evidence for our claims about stability, invariance to environment, and behavior as a causal detector.

@@

In the non linear case, sigmoid functions are...
FC: insert comment about scaling sigmoids, and maybe something about uniform coeffs
